---
title: "KHANDLE Codebook"
subtitle: "Wave 1 Summary"
# author: "Juliet Yixuan Zhou"
date: "07/14/2022"
output:
  word_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE}
library(tidyverse)
library(haven)
library(epiDisplay)
library(readxl)
```

```{r load dataset}
path_to_box <- "/Users/julietzhou/Library/CloudStorage/Box-Box/"
# update to the most recent data release
date <- "20220714"
path_to_folder <- "KHANDLE_coded_data/Raw_data_tables/All_Wave/transfer13_2022Jul15/"
dat <- read_sas(
  paste0(path_to_box, path_to_folder, "khandle_all_waves_", date, ".sas7bdat"))

dat_w1 <- dat %>% dplyr::select(STUDYID, starts_with("W1"), WAVE1)
# dat_w2 <- dat %>% dplyr::select(STUDYID, starts_with("W2"), WAVE2)
# dat_w3 <- dat %>% dplyr::select(STUDYID, starts_with("W3"), WAVE3)
# dat_lang <- dat %>% dplyr::select(STUDYID, starts_with("LANG"))
# dat_mhc <- dat %>% dplyr::select(STUDYID, starts_with("mhc"))
```

```{r load data dictionary, message=FALSE, warning=FALSE}
# load the data dictionary for variable name and variable description
dictionary <- read_excel(
  paste0(path_to_box, path_to_folder, 
         "KHANDLE_All_Waves_", date, "_Data_Dictonary.xlsx"), 
  .name_repair = "universal", 
  sheet = "Data_Description", skip = 4) %>%
  dplyr::select("PHI_check", 
                "Variable...Name", "Variable...Description", "Values") %>% 
  rename("var_name" = "Variable...Name", 
         "var_desc" = "Variable...Description", 
         "values"  = "Values")
```


\pagebreak

Note:

For each variable, the following information is pulled from the dictionary:

*	Variable name
*	Variable description
*	Possible values and coding

A frequency table is generated to accompany most of the variables, with the 
following columns:

*	Frequency
*	%(NA+) and cum.%(NA+): relative and cumulative frequencies calculated from 
  including the NA’s in the total
*	%(NA-) and cum.%(NA-): relative and cumulative frequencies calculated from 
  excluding the NA’s from the total

If a variable is quantitative in nature, a histogram is used to replace the 
frequency table, accompanied by the number of NA’s. 

\pagebreak

```{r codebook function}
codebook <- function(data, var, categorical = TRUE, print.values = TRUE) {
  var_description <- dictionary %>% 
    filter(var_name == var) %>% 
    # dplyr::select(var_desc)
    pull(var_desc)
  # var_description <- as.character(var_description)
  var_values <- dictionary %>% 
    filter(var_name == var) %>% 
    # dplyr::select(values)
    pull(values)
  # var_values <- as.character(var_values)
  # print out information to be included in the codebook
  
  print(str_c(var, ": ", var_description))
  if (!is.na(var_values) & print.values) {print(var_values)}
  
  if(categorical) {
    # print the frequency table
    # with absolute, relative and cumulative frequencies
    print(str_c("Frequency table of ", var))
    tab1(data[var], graph = FALSE, cum.percent = TRUE) %>% print()
  } else {
    x <- data[var] %>% as_vector()
    na_count <- sum(is.na(x))
    na_perc <- round(na_count/length(x), digits = 3)
    print(str_c("NA Frequency: ", na_count, " (", 100*na_perc, "%)"))
    try(hist(x, main = NULL, xlab = paste(var)))
  }
  
  cat("\n\n")
}
```

## Wave Information

<br>

```{r wave 1 info}
w1_wave_info_vars <- c("WAVE1", "W1_ENROLLED", "W1_COMPLETED_AT", 
                       "W1_TO_W2_DAYS", "W1_TO_W3_DAYS")
codebook(dat_w1, "WAVE1")
codebook(dat_w1, "W1_ENROLLED")
codebook(dat_w1, "W1_COMPLETED_AT")
codebook(dat_w1, "W1_TO_W2_DAYS", categorical = FALSE)
codebook(dat_w1, "W1_TO_W3_DAYS", categorical = FALSE)
all_vars <- w1_wave_info_vars
```

\pagebreak

## Age at Interview

<br>

```{r age at interview}
w1_age_at_intv <- "W1_INTERVIEW_AGE"
codebook(dat_w1, w1_age_at_intv, categorical = FALSE)
all_vars <- c(all_vars, w1_age_at_intv)
```

\pagebreak

## Education

<br>

```{r w1 education}
w1_edu_vars <- dat_w1 %>% names() %>% str_subset("W1_EDU|D_EDU")
for (var in w1_edu_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_edu_vars)
```

\pagebreak

## Occupational History

<br>

```{r w1 occupational history}
w1_jobs_vars <- dat_w1 %>% names() %>% 
  str_subset("WORK|JOB|_EMP_|MILLITARY") %>% 
  str_subset("VOLUNTEER", negate = TRUE)
codebook(dat_w1, "W1_FIRST_JOB_AGE")
codebook(dat_w1, "W1_FIRST_JOB_AGE_YEARS", categorical = FALSE)
for(var in w1_jobs_vars[3:24]) {
  codebook(dat_w1, var)
}
for(var in c(w1_jobs_vars[25:38], "W1_MILITARY")) {
  codebook(dat_w1, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_jobs_vars, "W1_MILITARY")
```

\pagebreak

## Volunteer Work

<br>

```{r}
w1_volunteer_vars <- dat_w1 %>% names() %>% str_subset("VOLUNTEER")
for(var in w1_volunteer_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_volunteer_vars)
```

\pagebreak

## Other Current Activities

<br>

```{r}
w1_ca_vars <- dat_w1 %>% names() %>% str_subset("_CA_")
for(var in w1_ca_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_ca_vars)
```

\pagebreak

## Ethnicity

<br>

```{r}
w1_ethn_vars <- dat_w1 %>% names() %>% str_subset("ETHNICITY|D_RACE")
for(var in w1_ethn_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_ethn_vars)
```

\pagebreak

## Immigration

<br>

```{r}
w1_immigration_vars <- dat_w1 %>% names() %>% 
  str_subset("COUNTRY_BORN|US_STATE|MX_STATE|AGE_MOVED_US|D_AGE_IMMIGRATION|MOTHER|FATHER")

for(var in w1_immigration_vars[1:4]) {
  codebook(dat_w1, var)
}
codebook(dat_w1, "W1_AGE_MOVED_US_AGE", categorical = FALSE)
for(var in w1_immigration_vars[6:15]) {
  codebook(dat_w1, var)
}
codebook(dat_w1, "W1_D_AGE_IMMIGRATION", categorical = FALSE)
all_vars <- c(all_vars, w1_immigration_vars)
```

\pagebreak

## Gender and Sexual Orientation

<br>

```{r}
w1_gender_vars <- dat_w1 %>% names() %>% str_subset("GENDER|ORIENTATION")
for(var in w1_gender_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_gender_vars)
```

\pagebreak

## Marital Status

<br>

```{r}
w1_marital_vars <- dat_w1 %>% names() %>% 
  str_subset("MARITAL|SPOUSE|DIVORCE|MARRIAGE")
for(var in w1_marital_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_marital_vars)
```

\pagebreak

## Income and Financial Insecurity

<br>

```{r}
w1_income_vars <- dat_w1 %>% names() %>% str_subset("INCOME")
for(var in w1_income_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_income_vars)
```

\pagebreak

## Residence History and Schools Attended

<br>

Some variables (including street address, city, and state) are marked PHI in the 
dictionary, and therefore not summarized here. 

```{r}
w1_res_vars <- dat_w1 %>% names() %>% str_subset("_RES_") 
w1_school_vars <- dat_w1 %>% names() %>% str_subset("_SCHOOL_") 
for(var in c(w1_res_vars, w1_school_vars)) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_res_vars, w1_school_vars)
```

\pagebreak

## Discrimination - Everyday

<br>

```{r}
w1_disc_day_vars <- dat_w1 %>% names() %>% str_subset("DISC_DAY") 
for(var in c("W1_DISCRIMINATION", w1_disc_day_vars)) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, "W1_DISCRIMINATION", w1_disc_day_vars)
```

\pagebreak

## Discrimination - Lifetime

<br>

```{r}
w1_disc_life_vars <- dat_w1 %>% names() %>% str_subset("DISC_LIFE") 
for(var in w1_disc_life_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_disc_life_vars)
```

\pagebreak

## Ladder

<br>

```{r}
codebook(dat_w1, "W1_LADDER1")
all_vars <- c(all_vars, "W1_LADDER1")
```

\pagebreak

## Children

<br>

```{r}
w1_children_vars <- dat_w1 %>% names() %>% 
  str_subset("CHILDREN") %>% 
  str_subset("CHILDHX", negate = TRUE)
for(var in w1_children_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_children_vars)
```

\pagebreak

## Siblings

<br>

```{r}
w1_siblings_vars <- dat_w1 %>% names() %>% str_subset("SIBLINGS") 
for(var in w1_siblings_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_siblings_vars)
```

\pagebreak

## Relatives

<br>

```{r}
w1_rel_vars <- dat_w1 %>% names() %>% str_subset("RELATIVES|_REL_") 
for(var in w1_rel_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_rel_vars)
```

\pagebreak

## Friends

<br>

```{r}
w1_friends_vars <- dat_w1 %>% names() %>% str_subset("FRIENDS") 
for(var in w1_friends_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_friends_vars)
```

\pagebreak

## Confidante

<br>

```{r}
w1_confidante_vars <- dat_w1 %>% names() %>% str_subset("CONFIDANTE") 
for(var in w1_confidante_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_confidante_vars)
```

\pagebreak

## Childhood Family History

<br>

```{r}
w1_childhx_vars <- dat_w1 %>% names() %>% str_subset("CHILDHX")
w1_mat_pat_vars <- dat_w1 %>% names() %>% str_subset("MATERNAL|PATERNAL")
w1_gu_vars <- dat_w1 %>% names() %>% str_subset("GROWINGUP")
for(var in c(w1_childhx_vars, w1_mat_pat_vars, w1_gu_vars)) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_childhx_vars, w1_mat_pat_vars, w1_gu_vars)
```

\pagebreak

## Health

<br>

```{r}
w1_equipment_vars <- dat_w1 %>% names() %>% str_subset("EQUIPMENT")
for(var in c("W1_HEALTH", w1_equipment_vars)) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, "W1_HEALTH", w1_equipment_vars)
```

\pagebreak

## Activities of Daily Living

<br>

```{r}
w1_adl_vars <- dat_w1 %>% names() %>% str_subset("DAILY_LIVING")
for(var in w1_adl_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_adl_vars)
```

\pagebreak

## Physical Activity

<br>

```{r}
w1_pa_vars <- dat_w1 %>% names() %>% str_subset("_PA_")
for(var in w1_pa_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_pa_vars)
```

\pagebreak

## Everyday Cognition

<br>

```{r}
w1_ecog_vars <- dat_w1 %>% names() %>% str_subset("_ECOG_")
for(var in w1_ecog_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_ecog_vars)
```

\pagebreak

## Sleep

<br>

```{r}
w1_sleep_vars <- dat_w1 %>% names() %>% str_subset("_SLEEP_")
for(var in w1_sleep_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_sleep_vars)
```

\pagebreak

## Self-Assessed Sensory Impairement

<br>

```{r}
w1_sensimp_vars <- dat_w1 %>% names() %>% str_subset("_SENSIMP_")
for(var in w1_sensimp_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_sensimp_vars)
```

\pagebreak

## Head Injury

<br>

```{r}
w1_headinj_vars <- dat_w1 %>% names() %>% str_subset("HEAD_INJURY")
w1_headtra_vars <- dat_w1 %>% names() %>% str_subset("HEAD_TRAUMA")
for(var in c(str_subset(w1_headinj_vars, "HOSP\\d"), 
             "W1_HEAD_INJURY_EXPLOSION", "W1_HEAD_TRAUMA")) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_headinj_vars, w1_headtra_vars)
```

The following block of questions, from W1_HEAD_TRAUMA_AGE_START to 
W1_HEAD_TRAUMA_DAZED are asked if HEAD_TRAUMA = 1:[Yes]. 

```{r}
for(var in str_subset(w1_headinj_vars, "HOSP\\d|EXPLOSION", negate = TRUE)) {
  codebook(dat_w1, var)
}
codebook(dat_w1, "W1_HEAD_TRAUMA_AGE_START")
codebook(dat_w1, "W1_HEAD_TRAUMA_AGE_START_TEXT", categorical = FALSE)
codebook(dat_w1, "W1_HEAD_TRAUMA_AGE_END")
codebook(dat_w1, "W1_HEAD_TRAUMA_AGE_END_TEXT", categorical = FALSE)
codebook(dat_w1, "W1_HEAD_TRAUMA_UNCONSCIOUS")
codebook(dat_w1, "W1_HEAD_TRAUMA_DAZED")
```

\pagebreak

## Pain

<br>

```{r}
w1_pain_vars <- dat_w1 %>% names() %>% str_subset("PAIN")
for(var in w1_pain_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_pain_vars)
```

\pagebreak

## Smoking

<br>

```{r}
w1_smk_vars <- dat_w1 %>% names() %>% str_subset("SMK")
for(var in w1_smk_vars[-3]) {
  codebook(dat_w1, var)
}
codebook(dat_w1, w1_smk_vars[3], categorical = FALSE)
all_vars <- c(all_vars, w1_smk_vars)
```

\pagebreak

## Alcohol Consumption

<br>

```{r}
w1_alc_vars <- dat_w1 %>% names() %>% str_subset("ALC")
for(var in w1_alc_vars) {
  codebook(dat_w1, var)
}
all_vars <- c(all_vars, w1_alc_vars)
```

\pagebreak

## Physical Measurements

<br>

```{r}
w1_phys_vars <- dat_w1 %>% names() %>% str_subset("_PHYS_")
w1_phys_cat <- rep(TRUE, length(w1_phys_vars))
w1_phys_cat[c(2,6:11,20,22:26,28,41:43)] <- FALSE
for(i in 1:length(w1_phys_vars)) {
  codebook(dat_w1, w1_phys_vars[i], w1_phys_cat[i])
}
all_vars <- c(all_vars, w1_phys_vars)
```

\pagebreak

## NIH Toolbox

<br>

```{r}
w1_NIHTLBX_vars <- dat_w1 %>% names() %>% str_subset("NIHTLBX")
codebook(dat_w1, "W1_NIHTLBX_NIH_Toolbox")
codebook(dat_w1, "W1_NIHTLBX_psmt_form")
for(var in str_subset(w1_NIHTLBX_vars, "NIH_Toolbox|form", negate = TRUE)) {
  codebook(dat_w1, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_NIHTLBX_vars)
```

\pagebreak

## SENAS

<br>

```{r}
w1_SENAS_vars <- dat_w1 %>% names() %>% str_subset("SENAS")
codebook(dat_w1, "W1_SENAS_SENAS")
codebook(dat_w1, "W1_SENAS_vmform")
codebook(dat_w1, "W1_SENAS_lsform")
codebook(dat_w1, "W1_SENAS_telephone")
for(var in str_subset(w1_SENAS_vars, "SENAS_SENAS|vmform|lsform|telephone", 
                      negate = TRUE)) {
  codebook(dat_w1, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_SENAS_vars)
```

\pagebreak

## Cognitive Impairment Probabilities 

<br>

```{r}
w1_COGIMP_PROB_vars <- dat_w1 %>% names() %>% str_subset("COGIMP_PROB")
for(var in w1_COGIMP_PROB_vars) {
  codebook(dat_w1, var, categorical = FALSE)
}
all_vars <- c(all_vars, w1_COGIMP_PROB_vars)
```

\pagebreak

## Interviewer Comments

<br>

The labels for these categorical comment variables are long and many share 
the same labels. These labels are detailed at the end of this section. 

```{r}
w1_INTFDBK_vars <- dat_w1 %>% names() %>% str_subset("INTFDBK")
all_vars <- c(all_vars, w1_INTFDBK_vars)
var_values_list <- c()
for(var in w1_INTFDBK_vars) {
  codebook(dat_w1, var, print.values = FALSE)
  var_value <- dictionary %>% 
    filter(var_name == var) %>% 
    pull(values)
  var_values_list <- c(var_values_list, var_value)
}
var_values_label <- unique(var_values_list)
var_label_index <- c()
for (i in 1:length(var_values_list)) {
  var_label_index <- c(var_label_index, 
                       match(var_values_list[i], var_values_label))
}
```

Values Label for Interviewer Comments:

```{r}
for (i in 1:length(var_values_label)) {
  print(paste0("Label ", i))
  print(var_values_label[i])
  cat("\n\n")
}
```

```{r}
tibble(
  "Variable" = w1_INTFDBK_vars,
  "Values Label" = var_label_index
) %>% print(n = Inf)
```

```{r check}
length(names(dat_w1))
names(dat_w1)[!names(dat_w1) %in% unique(all_vars)]
# all variables should be summarized in this codebook other than SUBJID
```