---
title: "STAR Codebook"
subtitle: "MRI Data Summary"
date: "09/01/2022"
output: 
  word_document: 
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r message=FALSE}
library(tidyverse)
library(haven)
library(epiDisplay)
library(readxl)
```

```{r load dataset and dictionary, message=FALSE, warning=FALSE, error=FALSE}
path_to_box <- "/Users/julietzhou/Library/CloudStorage/Box-Box/"
path_to_folder <- 
  "STAR_coded_data/Raw_data_tables/STAR_MRI_data/STAR_MRI_2022Sep01/"

# DTI data 
dat_DTI <- read.delim(
  paste0(path_to_box, path_to_folder, "summary_DTI_K-STAR_KHANDLE_082922_age.txt"), 
  header = TRUE, sep = ""
)

# dropping the fifth column, which I can only guess is
# BVALUE: number of diffusion volumes for each bvalue
# but the values are hard to interpret and therefore not summarized
dat_DTI_edit <- dat_DTI[, c(1,2,3,4,6,7,8)]
names(dat_DTI_edit) <- c("Study", "ID", "FW", "FA", "Site", "Age_at_Date", "Date_PreCovid")

# convert age, FW, and FA into numeric variables
dat_DTI_edit <- dat_DTI_edit %>% 
  mutate(
    Age_at_Date = as.numeric(Age_at_Date),
    FW = as.numeric(FW), 
    FA = as.numeric(FA))

# there are data entry errors for:
# ID = K028791 does not have FW and FA values
# ID = K076001 has wrong site format

# manually add in the correct entries
dat_DTI_edit <- dat_DTI_edit %>% 
  filter(!ID %in% c("K028791", "K076001")) %>% 
  add_row(
    tibble(Study = "khandle", ID = "K028791", Site = "IRC", 
           Age_at_Date = 85.84, Date_PreCovid = "0")) %>% 
  add_row(
    tibble(Study = "khandle", ID = "K076001", Site = "UC_Davis", 
           FW = 0.236069, FA = 0.554519, 
           Age_at_Date = 86.85, Date_PreCovid = "0"))

# T1 data
dat_T1 <- read_excel(
  paste0(path_to_box, path_to_folder, "k-star_T1_analysis_052322_age.xlsx"))
T1_var_labels <- tibble(
  variable = names(dat_T1)[-c(1,2)],
  label = c(
    "3DT1 Image Quality (Good, Fair, Unanalyzable)", 
    "FLAIR Image Quality (Good, Fair, Unanalyzable)",
    "MRI Scanner Magnetic Field Strength (3 Tesla)", 
    "MRI Scanner Manufacturer (SIEMENS)",
    "MRI Scanner Model Name (TrioTim or Skyra)",
    "Total Cranial Volume (Cubic Centimeters)",
    "Total Brain Volumn (Cubic Centimeters)", 
    "Total Cerebrospinal Fluid Volume (Cubic Centimeters)", 
    "Total Gray Matter Volume (Cubic Centimeters)", 
    "Total White Matter Volume (Cubic Centimeters)", 
    "Segmented Left Hippocampus Volume (Cubic Centimeters)", 
    "Segmented Right Hippocampus Volume (Cubic Centimeters)", 
    "Segmented Total Hippocampus Volume (Cubic Centimeters)", 
    "Segmented Left Lateral Ventricle Volume (Cubic Centimeters)", 
    "Segmented Right Lateral Ventricle Volume (Cubic Centimeters)", 
    "Segmented Total Lateral Ventricle Volume (Cubic Centimeters)", 
    "Segmented Third Ventricle Volume (Cubic Centimeters)", 
    "Segmented Frontal Cortical Gray Matter Volume (Cubic Centimeters)", 
    "Segmented Occipital Cortical Gray Matter Volume (Cubic Centimeters)", 
    "Segmented Parietal Cortical Gray Matter Volume (Cubic Centimeters)", 
    "Segmented Temporal Cortical Gray Matter Volume (Cubic Centimeters)", 
    "Total Cerebrospinal Fluid Volume (Cubic Centimeters)", 
    "Total Gray Matter Volume (Cubic Centimeters)",
    "Total White Matter Volume (Cubic Centimeters)", 
    "Total Cerebrum White Matter Hyperintensity Volumn (Cubic Centimeters)", 
    "Total Brain Volumn (Cubic Centimeters)",
    "Analysis Status", 
    "Age of participant at scan",
    "Scan: Pre-COVID"
  )
)

```

\pagebreak

Note:

For each variable, the following information is pulled from the dictionary:

*	Variable name
*	Variable description
*	Possible values and coding

A frequency table is generated to accompany most of the variables, with the 
following columns:

*	Frequency
*	%(NA+) and cum.%(NA+): relative and cumulative frequencies calculated from 
  including the NA’s in the total
*	%(NA-) and cum.%(NA-): relative and cumulative frequencies calculated from 
  excluding the NA’s from the total

If a variable is quantitative in nature, a histogram is used to replace the 
frequency table, accompanied by the number of NA’s. 

\pagebreak


# T1 dataset

```{r, eval = TRUE}
for (var in names(dat_T1)[-c(1,2)]) {
  if (var == "Status") {
    cat(str_c(var, ": Analysis Status"), "\n")
    tab1(dat_T1[var], graph = FALSE, cum.percent = TRUE) %>% print()
    
  } else if (var == "Date_Precovid") {
    cat(str_c(var, ": whether the scan was done before COVID-19 started."), "\n")
    cat("1 = pre-COVID, 0 = after start of COVID", "\n")
    tab1(dat_T1[var], graph = FALSE, cum.percent = TRUE) %>% print()
   
  } else if (var == "Age_at_Date") {
    cat(str_c(var, ": Age of participant at scan"), "\n")
    x <- dat_T1[var] %>% as_vector()
    hist(x, main = paste(var))
    
  } else if (var %in% c("_3DT1_QC", "FLAIR_QC", "Field_Strength", 
                        "Manufacturer","ModelName")) {
    var_description <- T1_var_labels %>% filter(variable == var) %>% pull(label)
    cat(str_c(var, ": ", var_description), "\n")
    tab1(dat_T1[var], graph = FALSE, cum.percent = TRUE) %>% print()
    
  } else {
    var_description <- T1_var_labels %>% filter(variable == var) %>% pull(label)
    cat(str_c(var, ": ", var_description), "\n")
    x <- dat_T1[var] %>% as_vector()
    hist(x, main = paste(var))
  }
  
  cat("\n\n")
}
```

# DTI dataset

```{r, eval = TRUE}
for (var in names(dat_DTI_edit)[-c(2)]) {
  if (var == "Date_PreCovid") {
    cat(str_c(var, ": whether the scan was done before COVID-19 started."), "\n")
    cat("1 = pre-COVID, 0 = after start of COVID", "\n")
    tab1(dat_DTI_edit[var], graph = FALSE, cum.percent = TRUE) %>% print()
      
  } else if (var == "Age_at_Date") {
    cat(str_c(var, ": Age of participant at scan"), "\n")
    x <- dat_DTI_edit[var] %>% as_vector()
    hist(x, main = paste(var))
    
  } else if (var %in% c("FW", "FA")) {
    label <- ifelse(var == "FW", 
                    paste0("FW: Free water fraction computed within voxels ", 
                           "from the WM mask (values between 0 and 1) \n"), 
                    paste0("FA: Fractional anisotropy computed within voxels ", 
                    "from the WM mask (values between 0 and 1) \n")
                    )
    cat(label)
    x <- dat_DTI_edit[var] %>% as_vector()
    hist(x, main = paste(var))
  } else {
    # study and site variables
    cat(paste0(var, "\n"))
    tab1(dat_DTI_edit[var], graph = FALSE, cum.percent = TRUE) %>% print()
  }

  cat("\n\n")
}


```